### 2016-09-29 syntax.tex
no message

Note that we do not require $\univ = 2^\elts$ since, e.g., a
set-membership data structure may only be defined for sets up to
some bounded size.

>>>>

Note that we do not require $\univ = 2^\elts$ since, e.g., a
particular set-membership data structure might only be defined for
sets up to some bounded size.
